Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
well balanced -> well-balanced

Representing a scene using a reduced set of representatives, with adapted similarity strategies allows us to improve ASSR performance compared to the BOF approaches based on GMMs which have been demonstrated to be equivalent to early integrations scheme on well balanced datasets \cite{lagrange:hal-01082501}. These results advocate for a hierarchical model of the scene, where short-time structure -- \ie below a second -- are represented using a convolutional network such as the scattering transform, whereas larger time scales -- \ie over a second -- are modeled as adaptive aggregates.

>>>>

Representing a scene using a reduced set of representatives, with adapted similarity strategies allows us to improve ASSR performance compared to the BOF approaches based on GMMs which have been demonstrated to be equivalent to early integrations scheme on well-balanced datasets \cite{lagrange:hal-01082501}. These results advocate for a hierarchical model of the scene, where short-time structure -- \ie below a second -- are represented using a convolutional network such as the scattering transform, whereas larger time scales -- \ie over a second -- are modeled as adaptive aggregates.
